\documentclass{resume}

\begin{document}
  % The following command is to avoid warnings.
  \hypersetup{pageanchor=false}

  \name{Mauricio Carrasco Ruiz}

  \vspace{1em}

  \contactPersonal%
      {\faMapMarker \ CDMX, México}
      {\faMobile \ XX XXXX XXXX}
      {\faEnvelopeO \ maucarrui@gmail.com}

  \vspace{1em}

  \contactSocial%
      {\faGithub
       \ \href{https://github.com/maucarrui}{github.com/maucarrui}}
      {\faLinkedinSquare
       \ \href{https://linkedin.com/in/maucarrui}{linkedin.com/in/maucarrui}}

  % Define two columns.
  \columnratio{0.6}
  \setlength{\columnsep}{2.5em}
  \begin{paracol}{2}
    
    \section{Education}
      
      \datedsubsection%
        {BSc in Computer Science}
        {2017-2022}
        
        \noindent
        National Autonomous University of Mexico (UNAM), \newline Mexico City,
        Mexico.

        \vspace{0.5em}
        
        \noindent
        Graduated with a grade of (9.77/10), corresponding to a 4.0 GPA. 

        \noindent
        \tit{In process of presenting my thesis defense.}

    \section{Experience}
    
      \subsection{\large{\tbf{Work}}}

      \experience%
          {Jr. Back-End Developer}
          {National Preparatory School No. 6 ``Antonio Caso''}
          {March 2017 - October 2017}
          {
            \begin{itemize}
            \item
              Volunteered for the development and maintenance of the web
              application responsible for the management of schedules and
              administration of subjects using \tbf{PHP} and \tbf{JavaScript}.
              
            \item
              Used technologies like \tbf{JQuery} and \tbf{MySQL} for the
              database administration.
            \end{itemize}
          }
        
      \experience%
          {Jr. Full-Stack Developer}
          {School of Engineering, UNAM}
          {June 2016 - November 2016}
          {
            \begin{itemize}
              \item Development and maintenance of an administration system for
                the \tit{XXXVII International Book Fair of the Palace of Mines}
                using the framework \tbf{Laravel PHP}.
                
              \item Responsible for the views that were shown to the client as
                well of its proper functionality with the database.
            \end{itemize}
          }

      \subsection{\large{\tbf{Academic and Investigation Projects}}}

      \project%
          {Tools for the Computational Handling of Graphs}
          {January 2022 - January 2023}
          {
            \begin{itemize}
              \item 
                Implemented several algorithms on \tbf{Java}, \tbf{Python}, and
                \tbf{Go} to work on Graph Theory.

              \item 
                Unit testing development.

              \item 
                Researched and designed optimal solutions to solve problems like
                the tree isomorphism problem and the doubly lexical ordering.
            \end{itemize}
          }
          
      \project%
          {Heuristics for Non-Deterministic Problems}
          {December 2020}
          {
            \begin{itemize}
              \item
                Implemented heuristics like the simmulated annealing and the ant
                colony on \tbf{C++}.

              \item Found good solutions on instances of problems like
                Travelling Salesman Problem (TSP), Generalized Assignment
                Problem (GAP), and the Minimum Vertex Cover Problem.
            \end{itemize}
          }

    \switchcolumn
      
    \section{Skills}
    
      \subsection{\tbf{Programming Languages}}

      \begin{tabular}{l l}
        $\bullet$ \ \tbf{Java}       & $\bullet$ \ \tbf{C/C++} \\
        $\bullet$ \ \tbf{Python}     & $\bullet$ \ \tbf{PHP}   \\
        $\bullet$ \ \tbf{JavaScript} & $\bullet$ \ \tbf{Go}    \\
      \end{tabular}

      \subsection{\tbf{Personal Skills}}
      
      \begin{itemize}
        \item Adaptive.
        \item Disciplined.
        \item Responsible.
        \item Self-learner.
        \item Time management.
      \end{itemize}

      \subsection{\tbf{Social Skills}}
      
      \begin{itemize}
        \item Empathic.
        \item Good communication.
        \item Problem solving.
        \item Team player.
      \end{itemize}
      
      \subsection{\tbf{Miscellaneous}}
      
      \begin{itemize}
        \item Web development.
          
          (\tbf{HTML}, \tbf{CSS}, \tbf{Node.js}).
          
        \item Database administration.
          
          (\tbf{Postgres}, \tbf{SQLite}, y \tbf{MySQL}).
          
        \item Frameworks.
          
          (\tbf{Django}, \tbf{Laravel PHP}, \tbf{Sails.js}).
          
        \item Version control with \tbf{Git}
          
        \item System administration with \tbf{Unix/Bash}.

        \item More than 2 years teaching programming and mathematics subjects at
          UNAM.

      \end{itemize}
      
    \section{Languages}
    
      \begin{itemize}
        \item Spanish (Native Speaker)
        \item English (C1)
      \end{itemize}
    
  \end{paracol}

\end{document}
